An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-05-24 EconGrowth.Rnw
Trying to fix error where CD with X fails for TZ.

@@

>>>>

\item{Heun: Fix error when calculating confidence intervals for Cobb-Douglas model for TZ with X. The problem occurs in function \texttt{cobbDouglasData}. To repeat the problem, call \texttt{cobbDouglasData(countryAbbrev="TZ", energyType="X")}}

@@

<<FindError, eval=TRUE>>=
# print(cobbDouglasCountryRow(countryAbbrev="US", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="UK", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="JP", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="CN", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="ZA", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="SA", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="IR", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="TZ", energyType="X"))

print(cobbDouglasData(countryAbbrev="TZ", energyType="X"))

# print(cobbDouglasModel(countryAbbrev="TZ", energyType="X"))
# print(cdeModel(countryAbbrev="TZ", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="ZM", energyType="X"))
@
